# Population

<!--Description -->

## Name

-   Small Area Population Estimates (SAPE) from the National Records of Scotland
-   Mid-2020 Population Estimates Scotland

## Year

2021 (Based on June 2020)

## Metadata

-   SAPE2017: 2017 NRS small area population estimates (Count)
-   WAPE2017: 2017 NRS small area population estimates and state pension age (Count)
-   Mid-2020 Population Estimates Scotland (Count). Detailed Metadata regarding the metrics, accuracy, and completeness are all linked [here](https://www.nrscotland.gov.uk/files//statistics/population-estimates/mid-20/mid-year-pop-est-20-metadata.pdf)
    -   Age

    -   Gender

## Source

-   Small area estimates: <https://www.nrscotland.gov.uk/statistics-and-data/statistics/statistics-by-theme/population/population-estimates/2011-based-special-area-population-estimates/small-area-population-estimates>
-   Scotland Mid-2020 by age and gender: [https://www.nrscotland.gov.uk/statistics-and-data/statistics/statistics-by-theme/population/population-estimates/mid-year-population-estimates/mid-2020](https://www.nrscotland.gov.uk/statistics-and-data/statistics/statistics-by-theme/population/population-estimates/mid-year-population-estimates/mid-2020#){.uri}

## Examples

```{r echo=F, message=F, out.width="100%", fig.cap="2017 NRS small area population estimates."}
library(sf)
library(dplyr)
read_sf("SG_SIMD_2020/SG_SIMD_2020.shp") %>% 
  filter(LAName == "Glasgow City") -> glasgowmap

plot(glasgowmap[4], main = "")
```

하이 헬로우 안녕

```{r echo=F, message=F}
library(kableExtra)
#Top 10
glasgowmap %>% 
  select(DataZone, DZName, SAPE2017) %>% 
  arrange(desc(SAPE2017)) %>% 
  st_drop_geometry() %>% 
  head(10) %>% 
  kbl()%>%
  kable_styling()
```
